\documentclass[12pt,letterpaper]{exam}
\RequirePackage{amssymb, amsfonts, amsmath, latexsym, verbatim, xspace, setspace, mathrsfs}
\usepackage{amsmath,amsthm,amssymb,amsfonts, 
hyperref, color, graphicx, enumitem}
\RequirePackage{tikz, pgflibraryplotmarks}
\usepackage{geometry}
\usepackage{graphicx}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
 \everymath{\displaystyle}
\newenvironment{problem}[2][Problem:]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2}]}{\end{trivlist}}

\newenvironment{claim}[2][Claim:]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2}]}{\end{trivlist}}

\newenvironment{defn}[2][Definition:]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2}]}{\end{trivlist}}

% Here's where you edit the Class, Exam, Date, etc.
\newcommand{\class}{Calculus 1 for Social Sciences}
\newcommand{\term}{Winter 2019}
\newcommand{\examnum}{}
\newcommand{\examdate}{Exam 2}
\newcommand{\timelimit}{90 min}

% For an exam, single spacing is most appropriate
\singlespacing
% \onehalfspacing
% \doublespacing

% For an exam, we generally want to turn off paragraph indentation
\parindent 0ex

\begin{document} 

% These commands set up the running header on the top of the exam pages
\pagestyle{head}
\firstpageheader{Name:}{Exam 2}{}
\runningheader{\class}{\examnum\ - Page \thepage\ of \numpages}{\examdate}
\runningheadrule

\begin{flushright}
\begin{tabular}{p{2.8in} r l}
\textbf{\class} & \textbf{Name:} & \makebox[2in]{\hrulefill}\\
\textbf{\term} &&\textbf{\examnum}\\
\textbf{\examdate} &&
\textbf{Time Limit: \timelimit}  \\ 
\end{tabular}\\
\end{flushright}
\rule[1ex]{\textwidth}{.1pt}




\begin{minipage}[t]{3.7in}
\vspace{0pt}
\begin{itemize}

\item \textbf{DO NOT open the exam booklet until you are told to begin. You should write your name and section number at the top and read the instructions.}

\vfill

\item Organize your work, in a reasonably neat and coherent way, in
the space provided. If you wish for something to not be graded, please strike it out neatly. I will grade only work on the exam paper, unless you clearly indicate your desire for me to grade work on additional pages.


\item You needn't spend your time rewriting definitions or axioms on the exam.

\item {\bf Show all your work.  Correct answers without supporting work may not receive credit.}
  
\end{itemize}


\end{minipage}
\hfill
\begin{minipage}[t]{2.3in}
\vspace{0pt}
%\cellwidth{3em}
\gradetablestretch{2}
%Uncomment this line to make the table display 100 as the total no matter what. This is good for tests with an ommit question.
%\settabletotalpoints{100}
\vqword{Problem}
\addpoints % required here by exam.cls, even though questions haven't started yet.	
\gradetable[v]%[pages]  % Use [pages] to have grading table by page instead of question

\end{minipage}

\begin{itemize}

\item When you have completed your test, hand it to me and have a great night.


\end{itemize}

\newpage

\begin{questions}
\addpoints
\question[5] Find $dy/dx$ by implicit differentiation for the  expressions $x^2y^{1/2} = x+2y^3$
  \vfill

\question[8] find the second derivative of the function $\displaystyle f(x) = \sqrt{3x+1}$ 
  \vfill
  
\question[7] Find the equation of the tangent line to the function defined by the equation $4x^2 + 9y^2 = 16$ at the point $(2,2\sqrt{5})$
\vfill

\newpage
\addpoints

\question Compute the derivatives of the following functions.  Show all of your work.
\begin{parts}
\part[5] $f(x) = (3x^2+2x+1)^{-2}$
\vfill
\part[5] $g(x) = \displaystyle\sqrt{\frac{2x+1}{2x-1}}$
\vfill
\end{parts}


\newpage 
\addpoints

\question[10] A car leaves an intersection traveling west its position 4 sec later is 20 ft from the intersection.  At the same time, another car leaves the same intersection heading north so that its position 4 sec later is 28 ft from the intersection.  If the speeds of the cars at that instant of time are 8 ft/sec and 11 ft/sec, respectively, find the rate at which the distance between the two cars is changing.
\vfill

\newpage
\addpoints
\question The weekly demand for LED tvs is $p = 600-0.5x$, where $p$ denotes the wholesale unit price in dollars and $x$ denotes the quantity demanded.  The weekly total costs function is given by $C(x) = 0.000002x^3 - 0.03x^2 + 400x + 80000$ where $C(x)$ denotes the the total cost incurred in producing $x$ sets.
\begin{parts}
  \part[4] find the revenue function and profit function.
\vfill
  \part[4] find the marginal cost function and the marginal revenue function.
\vfill
  \part[2] Compute $C'(2000)$ and $R'(2000)$ and interpret your results.
\vfill
  \part[4] Find the average cost function.
\vfill
  \part[4] Find the marginal average cost function.
\vfill
  \part[2] Compute $\bar{C}'(500)$ and $\bar{C}'(10000)$ and interpret your results.
\vfill
\end{parts}




\end{questions}
\end{document}
